---
title: "Analyze_networks"
author: "Christian Ayala Ortiz"
date: "`r Sys.Date()`"
output: html_document
---

# 1. Loading libraries

```{r setup}
library(patchwork)
library(ggpubr)
library(igraph)
library(ggfx)
library(ggh4x)
library(ggnetwork)
library(readxl)
library(MetaNet)
library(tidyverse)
library(ggClusterNet)
source('scripts/custom_functions.R')
```

## Load data

```{r}
colors <- c('Wet' = '#20a39e',
            'Dry' = '#ffba49')

mag_taxonomy <- load_mag_taxonomy()

bin_code <- read_csv('data/networks/mag_network_names_updated.csv')

phyla_colors <- set_names(get_palette('Paired', 18),
                          nm =sort(unique(mag_taxonomy$Phylum)))

phyla_colors[3] = 'blue'
```

# 2. Co-ocurrence network

## 2.1 Nodes

```{r}
nodes_wet <- read_csv('data/networks/nodes_mags_wet.csv') %>% 
  mutate(net = 'Wet') %>% 
  inner_join(bin_code, by = c('Name' = 'ID'))

nodes_dry <- read_csv('data/networks/nodes_mags_dry.csv') %>% 
  mutate(net = 'Dry') %>% 
  inner_join(bin_code, by = c('Name' = 'ID'))

nodes_all <- rbind(nodes_wet, nodes_dry) 
```

## 2.2 Edges

```{r}
edges_wet <- read_csv('data/networks/edges_mags_wet.csv') %>% 
  mutate(net = 'Wet')
edges_dry <- read_csv('data/networks/edges_mags_dry.csv') %>% 
  mutate(net = 'Dry')

edges_all <- rbind(edges_wet, edges_dry) %>% 
  mutate(interaction = ifelse(interaction == 'pp', 'Positive', 'Negative'))
```

## 2.3 Networks

```{r}
mag_phyl <- mag_taxonomy %>% 
  mutate(Phylum = str_remove(Phylum, 'p__'),
         Phylum_lump = fct_lump_n(Phylum, n = 10))

nodes_ready <- nodes_all %>% 
  group_by(`No.module`) %>% 
  mutate(nodes_per_module = n(),
         module = paste0('Module ', `No.module`),
         module = factor(module, levels = paste0('Module ', 0:21)),
         node_topological_role = case_when(Zi <= 2.5 & Pi <= 0.62 ~ "Peripherals",
                                           Zi <= 2.5 & Pi > 0.62 ~ "Connectors",
                                           Zi > 2.5 & Pi <= 0.62 ~ "Module hubs",
                                           Zi > 2.5 & Pi > 0.62 ~ "Network hubs")) %>% 
  inner_join(mag_phyl, by = c('Genome' = 'bin')) %>% 
  ungroup()

i <- 1
module_colors <- map_chr(levels(nodes_ready$module), function(mod){
  n <- nodes_ready %>% 
    filter(module == mod) %>% 
    pull(nodes_per_module) %>% 
    unique
  
  if(n > 10){
    col <- get_palette('Dark2', 6)[i]
    i <<- i +1
  } else {
    col = 'transparent'
  }
  
  return(col)
})

names(module_colors) <- levels(nodes_ready$module)

phyl_colors <- set_names(get_palette('Paired', 11),
                         nm = sort(unique(nodes_ready$Phylum)))

nodes_split <- nodes_ready %>% 
  split(.$net)

edges_split <- edges_all %>% 
  split(.$net)

graph_rmt <- map2(nodes_split, edges_split, function(nod, edg){
  
  nod2 <- select(nod, Name, Phylum, node_topological_role, module, node.degree)
  graph_from_data_frame(edg, directed = FALSE, vertices = nod2)
})

single_net_df <- imap(graph_rmt, function(x, net_name){
  ggnetwork(x) %>% 
    mutate(origin = net_name)
}) %>% 
  reduce(rbind)

single_net_plot <- single_net_df %>% 
  mutate(node_size = node.degree/max(node.degree) * .5) %>% 
  ggplot(aes(x = x,
             y = y,
             xend = xend,
             yend = yend)) +
  ggforce::geom_mark_ellipse(aes(group = module,
                                 fill = module),
                             color = 'transparent',
                             show.legend = FALSE,
                             alpha = .1) +
  scale_fill_manual(values = module_colors) +
  with_outer_glow(
    geom_nodes(data = . %>% filter(node_topological_role == 'Connectors'),
               aes(x = x,
                   y = y,
                   shape = node_topological_role,
                   size = node_size),
               show.legend = FALSE),
    colour = 'red',
    sigma = 5,
    expand = 7
  ) +
  #labs(title = paste0(name, ' months')) +
  facet_wrap(~origin) +
  geom_edges(aes(color = interaction)) +
  scale_color_manual(values = c('steelblue', 'indianred2')) +
  scale_size_continuous(range = c(.5, 2)) +
  ggnewscale::new_scale_fill() +
  geom_nodes(aes(fill = Phylum,
                 shape = node_topological_role,
                 size = node_size),
  ) +
  scale_fill_manual(values = phyla_colors) +
  scale_shape_manual(values = c('Connectors' = 23, 
                                'Network hubs' = 24, 
                                'Peripherals' = 21)) +
  labs(title = 'Co-ocurrence networks') +
  guides(fill = guide_legend(override.aes = list(shape = 21))) +
  guides(size = 'none') +
  theme_blank() +
  theme(legend.position = 'none',
        plot.title = element_text(face = 'bold', hjust = 0.5, size = 7),
        strip.background = element_blank(),
        strip.text = element_text(size = 6))

single_net_plot
```

# 2. Metabolic interactions network

## 2.1 All data

```{r}
global_results <- read_tsv('data/networks/smetana_pairs_res_summarized.tsv', 
                           col_names = c('community', 'medium', 
                                         'size', 'mip', 'mro', 'comparison')) %>% 
  mutate(comparison = str_remove(comparison, '_results.*'),
         MAG_1 = str_extract(comparison, '.*_[0-9]+(?=_(bco|bcn|DNA))'),
         MAG_2 = str_extract(comparison, '(?<=[0-9]_)(bco|bcn|DNA).*'),
         mip = as.numeric(mip),
         mro = as.numeric(mro))

detailed_results <- read_tsv('data/networks/smetana_pairs_detailed_2_13.tsv',
                             col_names = c('community', 'medium', 
                                           'receiver', 'donor', 'compound',
                                           'scs', 'mus', 'mps', 'smetana', 'file')) %>% 
  mutate(comparison = map2_chr(donor, receiver, function(x, y){
    x <- str_remove(x, '_genes_model')
    y <- str_remove(y, '_genes_model')
      str_c(sort(c(x, y)), collapse = '_')
  }))

receiver_counts <- detailed_results %>% 
  group_by(receiver) %>% 
  count(name = 'receiver_counts')

donor_counts <- detailed_results %>% 
  group_by(donor) %>% 
  count(name = 'donor_counts')

donor_or_receiver <- full_join(receiver_counts, donor_counts, by = c('receiver' = 'donor')) %>% 
  rename(bin = receiver) %>% 
  mutate(across(c(receiver_counts, donor_counts), ~ifelse(is.na(.x), 0, .x)),
         main_role = ifelse(receiver_counts > donor_counts, 'Receiver', 'Donor'),
         bin = str_remove(bin, '_genes.*'))

global_filtered <- global_results %>% 
  filter(mip >= 5)

detailed_results_filtered <- detailed_results %>% 
  filter(!(comparison %in% global_filtered$comparison))

edges <- global_filtered %>% 
  filter(mip >= 5) %>% 
  select(from = MAG_1, to = MAG_2, mip)

nodes <- tibble(Name = unique(c(edges$from, edges$to))) %>% 
  inner_join(mag_taxonomy, by = c('Name' = 'bin')) %>% 
  inner_join(donor_or_receiver, by = c('Name' = 'bin'))
```

## 2.2 Filtering for those in the dry and wet networks

```{r}
nodes_met_dry <- nodes %>% 
  filter(Name %in% nodes_dry$Genome)

edges_met_dry <- edges %>% 
  filter((from %in% nodes_met_dry$Name & to %in% nodes_met_dry$Name))

nodes_met_wet <- nodes %>% 
  filter(Name %in% nodes_wet$Genome)

edges_met_wet <- edges %>% 
  filter((from %in% nodes_met_wet$Name & to %in% nodes_met_wet$Name))
```

## 2.3 Create graph objects

```{r}
dry_met_network <- create_network_zipi(edges_met_dry, nodes_met_dry)
wet_met_network <- create_network_zipi(edges_met_wet, nodes_met_wet)
```

## 2.4 Plotting as facets

```{r}
met_list <- list('Dry' = dry_met_network,
                 'Wet' = wet_met_network)

roles_df <- tibble(role_name = c("Peripherals", "Network hubs", "Module hubs", "Connectors"),
                   roles = 1:4)

met_net_df <- imap(met_list, function(graph, net_name){
  lay <- layout_on_sphere(graph)
  df <- ggnetwork(graph, layout = lay[,c(1,2)]) %>% 
    mutate(origin = net_name) %>% 
    mutate(roles = as.integer(roles)) %>% 
    left_join(roles_df)
}) %>% reduce(rbind)


met_network <- met_net_df %>% 
  mutate(node_size = Degree/max(Degree) * .5) %>% 
  ggplot(aes(x = x,
             y = y,
             xend = xend,
             yend = yend)) +
  geom_edges(data = . %>% filter(connection_with == 'Link with other MAG'),
             color = 'gray20',
             linewidth = .03) +
  geom_edges(data = . %>% filter(connection_with == 'Link with hubs'),
             color = 'gray20',
             linewidth = .03) +
  ggnewscale::new_scale_color() +
  with_outer_glow(
    geom_nodes(data = . %>% filter(role_name %in% c('Network hubs')),
               aes(x = x,
                   y = y,
                   size = node_size),
               shape = 24),
    colour = 'red2',
    sigma = 5,
    expand = 7
  ) +
  geom_nodes(aes(fill = Phylum,
                 shape = role_name,
                 size = node_size)) +
  facet_wrap(~origin) +
  scale_shape_manual(values = c('Connectors' = 23, 
                                'Network hubs' = 24, 
                                'Peripherals' = 21)) +
  scale_fill_manual(values = phyla_colors) +
  guides(fill = guide_legend(override.aes = list(shape=21)),
         size = 'none') +
  labs(title = 'Metabolic Interaction Potential network') +
  scale_size_continuous(range = c(1.5, 4)) +
  theme_blank() +
  theme(legend.position = 'bottom',
        plot.title = element_text(face = 'bold', hjust = 0.5, size = 9),
        strip.background = element_blank(),
        strip.text = element_text(size = 6),
        legend.text = element_text(size = 7),
        legend.title = element_text(size = 9),
        legend.title.position = 'top',
        legend.key.spacing.y = unit(.01, 'lines'),
        legend.key.spacing.x = unit(.5, 'lines'),
        legend.key.size = unit(0, 'lines'))


met_network
```

# 4. Shared metabolites

## 4.1 Classifying metabolites

```{r}
bigg_metabolites_complete <- read_tsv('data/networks/bigg_metabolites.tsv') 

bigg_metabolites <- bigg_metabolites_complete %>% 
  select(universal_bigg_id, name) %>% 
  distinct()

detailed_metabolites <- detailed_results %>% 
  select(compound) %>% 
  distinct() %>% 
  mutate(compound = str_remove_all(compound, 'M_|_e')) %>% 
  inner_join(bigg_metabolites, by = c('compound' = 'universal_bigg_id'))

classified  <-  list(`nitrogen\nmetabolites` = c('no3', 'no2', 'n2', 'nh3', 
                                                 'n2o', 'nh4',
                                                 'no', 'hae', 'urea') %>% 
                       str_c('M_', ., '_e'),
                     
                     `amino\nacids` = c('arg__L', 'his__L', 'lys__L', 
                                        'asp__L', 'glu__L', 'ser__L', 
                                        'thr__L', 'asn__L', 'gln__L', 
                                        'cys__L', 'selcys', 'gly', 
                                        'pro__L', 'ala__L', 'val__L', 
                                        'ile__L', 'leu__L', 'met__L', 
                                        'phe__L', 'tyr__L', 'trp__L', 
                                        'orn', 'orn__L', 'hom__L', 'argp',
                                        'asp__D', 'agm', 'glyb', 'citr__L', 
                                        'ala__D')  %>% 
                       str_c('M_', ., '_e'),
                     
                     `sulfur\nmetabolites`  = c('so4', 'aps', 'paps', 'so3', 
                                                'h2s', 'tsul', 'acser',
                                                'cys__L', 's', 'ch4s') %>% 
                       str_c('M_', ., '_e'),
                     
                     peptides  = c('LalaDgluMdap', 'alaala', 'cgly', 
                                   'etha')  %>% 
                       str_c('M_', ., '_e'),
                     
                     sugars  = c('rib', 'cellb', 'glc__D', 'inost', 'man1p', 
                                 'lcts', 'f6p',
                                 'gal', 'abt__L', 'xyl__D', '6pgc', 'galur', 
                                 'glcn', 'g6p_B',
                                 'arab__D', 'dha', 'mnl1p')  %>% 
                       str_c('M_', ., '_e'),
                     
                     aromatics  = c('tol', 'glyald', 'bz', 'indole', 
                                    '4abz', 'pacald', '4hba', '4hbz',
                                    'pea', 'bzal', 'pac', 'catechol', 
                                    'id3acald')  %>% 
                       str_c('M_', ., '_e'),
                     
                     `carboxylic\nacids`  = c('oxa', 'acac', 'ac', 'cit', 
                                              'lac__L', 'mal__L', 'fum',
                                              'akg')  %>% 
                       str_c('M_', ., '_e'),
                     
                     `fatty acids\nand related`  = c('for', '2obut', 
                                                     'ppap', 'actn__R', 
                                                     '4abut', 'succ',
                                                     'R_3hhdca', 'glcr', 
                                                     'galct__D', 'ocdcea', 'bhb',
                                                     'R_3hdcaa',
                                                     'R_3hocta', 
                                                     'R_3hdda', 
                                                     'R_3hhxa', 'R_3httdca', 
                                                     'R_3hpt',
                                                     'R_3htd5e')  %>% 
                       str_c('M_', ., '_e'),
                     
                     `purine, pirimidine\nand derivatives`  = c('hxan', 
                                                                'gua', 'thym', 
                                                                'thymd', 'ura',
                                                                'xan', 'ins', 
                                                                'ads', 'gsn', '3cmp',
                                                                '3gmp', 
                                                                '3amp', 'cytd')  %>% 
                       str_c('M_', ., '_e'),
                     
                     alcohol  = c('etoh', '12ppd__R', 'meoh', 
                                  '12ppd__S', 'btd_RR')  %>% 
                       str_c('M_', ., '_e'),
                     
                     `vitamins, cofactors\nand related`  = c('nac', 'pnt__R', 
                                                             'thm', 'ncam', 'pydxn',
                                                             'gthrd')  %>% 
                       str_c('M_', ., '_e'),
                     
                     siderophore  = c('salchs4fe', 'fe3pyovd_k', 
                                      'istfrnA', 'pyovd_kt', 'fe3dcit',
                                      'istfrnB', 'stfrnA', 'stfrnB')  %>% 
                       str_c('M_', ., '_e'),
                     
                     other  = c('anhgm', 'coa', 'co2', 'h2o2', 'ptrc', 'spmd',
                                'udcpp', 'co', 'forglu', 'gam6p', 
                                'acgam1p', 'o2', 'R_3hcmrs7e',
                                '5dglcn', '2dglcn', 'acald', 'hco3', 
                                'pheme', 'glyclt', 'chol',
                                'quin', 'tre6p', 'acglu', 'diact', 
                                'dxylnt', 'fald', 'ppal', '4abutn',
                                'gcald', '4hpro_LT', 'cell4')  %>% 
                       str_c('M_', ., '_e'),
                     
                     `lipids\nand related`  = c('g3pe', 'g3pg', 'glyc', 
                                                'glyc3p', 'dhap')  %>% 
                       str_c('M_', ., '_e'))

classified_df <- imap(classified, function(x, y){
  
  df <- tibble(compound = x) %>% 
    mutate(group = y)
  
}) %>% reduce(rbind)

```

## 4.2 Plot of hubs

```{r}
hubs <- met_net_df %>% 
  filter(role_name == 'Network hubs') %>%
  pull(name) %>% 
  unique()

detailed_filtered_hubs <- detailed_results %>% 
  mutate(across(c(receiver, donor), ~str_remove(.x, '_genes.*'))) %>% 
  filter(smetana > 0.1 | compound %in% classified$nitrogen_metabolites |
           compound %in% classified$sulfur_metabolites,
         receiver %in% hubs | donor %in% hubs,
         !(receiver %in% hubs & donor %in% hubs)) %>% 
  mutate(interaction_role = ifelse(receiver %in% hubs, 'Receives', 'Donates'),
         hub_bac = ifelse(interaction_role == 'Receives', receiver, donor),
         companion_bac = ifelse(interaction_role == 'Receives', donor, receiver)) %>% 
  inner_join(mag_taxonomy, by = c('companion_bac' = 'bin')) %>% 
  group_by(hub_bac, interaction_role, Phylum, compound) %>% 
  count() %>% 
  inner_join(classified_df) %>% 
  mutate(compound = str_remove_all(compound, 'M_|_e')) %>% 
  left_join(bigg_metabolites, by = c('compound' = 'universal_bigg_id')) %>% 
  inner_join(mag_taxonomy %>% select(bin, Phylum_hub = Phylum), by = c('hub_bac' = 'bin'))


wet_mags <- met_net_df %>% 
  filter(origin == 'Wet') %>% 
  pull(name) %>% 
  unique()

dry_mags <- met_net_df %>% 
  filter(origin == 'Dry') %>% 
  pull(name) %>% 
  unique()

ll <- list(Dry = dry_mags,
           Wet = wet_mags)

all_sharing <- imap(ll, function(mags, or){
  df <- detailed_results %>% 
    mutate(across(c(receiver, donor), ~str_remove(.x, '_genes.*'))) %>% 
    filter(smetana > 0.1 | compound %in% classified$nitrogen_metabolites |
             compound %in% classified$sulfur_metabolites,
           receiver %in% mags & donor %in% mags) %>% 
    inner_join(mag_taxonomy %>% 
                 select(bin, 
                        Phylum_donor = Phylum,
                        Class_donor = Class), by = c('donor' = 'bin')) %>% 
    inner_join(mag_taxonomy %>% 
                 select(bin, 
                        Phylum_receiver = Phylum,
                        Class_receiver = Class), by = c('receiver' = 'bin')) %>% 
    inner_join(classified_df) %>% 
    mutate(compound = str_remove_all(compound, 'M_|_e')) %>%
    left_join(bigg_metabolites, by = c('compound' = 'universal_bigg_id')) %>% 
    select(donor, Phylum_donor, Class_donor,
           receiver, Phylum_receiver, Class_receiver, compound,
           name, group) %>% 
    mutate(network = or)
})

all_sharing_df <- reduce(all_sharing, rbind)

write_csv(all_sharing_df, 'docs/all_shared_metabolites.csv')

shared_metabolites_plot <- detailed_filtered_hubs %>% 
  mutate(net = ifelse(hub_bac == 'bco_bin_18_1', 'Wet MPI network', 'Dry MPI network'),
         hub_bac = str_c(hub_bac, '\n', Phylum_hub)) %>% 
  filter(group %in% c('amino\nacids', 'aromatics', 
                      'nitrogen\nmetabolites',
                      # 'sulfur\nmetabolites', 
                      # 'carboxylic\nacids', 
                      # 'fatty acids\nand related', 
                      'sugars')) %>% 
  mutate(name = case_when(str_detect(name, 'Arabinose') ~ 'D-Arabinose',
                          str_detect(name, 'Fructose') ~ 'D-Fructose-6P',
                          str_detect(name, 'gluconate') ~ '6P-gluconate',
                          TRUE ~ name)) %>% 
  ggplot() +
  geom_tile(aes(x = Phylum,
                y = name,
                fill = Phylum_hub),
            color = 'white',
            show.legend = FALSE) +
  facet_grid2(cols = vars(net, hub_bac,interaction_role),
              rows = vars(group),
              scales = 'free',
              space = 'free',
              strip = strip_nested(size = 'variable',
                                   clip = 'off',
                                   text_y = elem_list_text(
                                     angle = c(rep(90, 7),
                                               rep(0, 37))
                                   )),
              switch = 'y') +
  scale_fill_manual(values = phyla_colors) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1, size = 5),
        strip.text.y.left = element_text(size = 5),
        plot.title = element_text(face = 'bold', hjust = 0.5),
        axis.text.y = element_text(size = 5),
        strip.text.x = element_text(size = 5),
        legend.text = element_text(size = 5),
        legend.title = element_text(size = 7),
        axis.title = element_blank(),
        strip.background = element_blank(),
        strip.placement = 'outer',
        panel.spacing = unit(0.05, 'lines'))

shared_metabolites_plot
```

# 5. Merging

## 5.1 Creating legend for networks

```{r}
leg_plot <- tibble(Phylum = unique(single_net_df$Phylum),
                   `Topological role` = c(rep('Connectors', 3), 
                                          rep('Peripherals', 4), 
                                          rep('Network hubs', 4))) %>% 
  ggplot() +
  geom_point(aes(x = Phylum,
                 y = `Topological role`,
                 fill = Phylum,
                 shape = `Topological role`)) +
  scale_shape_manual(values = c('Connectors' = 23, 
                                'Network hubs' = 24, 
                                'Peripherals' = 21)) +
  scale_fill_manual(values = phyla_colors) +
  
  geom_hline(aes(yintercept = 1,
                 color = 'Negative')) +
  geom_hline(aes(yintercept = 2,
                 color = 'Positive')) +
  scale_color_manual(values = c('Negative' = 'steelblue', 
                                'Positive' = 'indianred2'),
                     guide = guide_legend(nrow = 3)) +
  labs(color = 'Correlation\n(Co-ocurrence network)') +
  guides(fill = guide_legend(override.aes = list(shape=21)),
         shape = guide_legend(nrow = 3)) +
  theme_blank() +
  theme(legend.position = 'bottom',
        legend.title.position = 'top',
        strip.text = element_text(size = 5),
        legend.text = element_text(size = 5),
        legend.title = element_text(size = 5),
        legend.key.spacing.y = unit(.01, 'lines'),
        legend.key.spacing.x = unit(.5, 'lines'),
        legend.key.size = unit(0, 'lines'))

leg_ready <- get_legend(leg_plot)
```

## 5.2 Merging Figure

```{r}
lay <- "
AB
CC
DD
"

fig5 <- single_net_plot + met_network + leg_ready + 
  free(shared_metabolites_plot) +
  plot_layout(design = lay,
              heights = c(1,.1,1.7)) +
  plot_annotation(tag_levels = list(c('A', 'B', '', 'C')))

ggsave('output_figures/Figure_5.svg', fig5, dpi = 300, 
       height = 185, width = 180, units = 'mm')
```

# Supplementary Table 2

## Network level index

```{r}

co_dry_netindex <- network_stats(graph_rmt$Dry) %>% 
  mutate(net = 'Dry',
         type = 'Co-occurrence')

co_wet_netindex <- network_stats(graph_rmt$Wet) %>% 
  mutate(net = 'Wet',
         type = 'Co-occurrence')

met_dry_netindex <- network_stats(dry_met_network) %>% 
  mutate(net = 'Dry',
         type = 'Metabolic')

met_wet_netindex <- network_stats(wet_met_network) %>% 
  mutate(net = 'Wet',
         type = 'Metabolic')

all_netindex <- rbind(co_dry_netindex, co_wet_netindex,
                      met_dry_netindex, met_wet_netindex) %>% 
  filter(!(index %in% c('num.pos.edges', 'num.neg.edges'))) %>% 
  unite(Network, type, net, sep = ' - ') %>% 
  pivot_wider(names_from = Network, values_from = value) 

all_netindex_final <- all_netindex %>% 
  add_row(index = 'num.positive.edges',
          `Co-occurrence - Dry` = edges_dry %>% filter(interaction == 'pp') %>% nrow,
          `Co-occurrence - Wet` = edges_wet %>% filter(interaction == 'pp') %>% nrow,
          .before = 2) %>% 
  add_row(index = 'num.negative.edges',
          `Co-occurrence - Dry` = edges_dry %>% filter(interaction == 'np') %>% nrow,
          `Co-occurrence - Wet` = edges_wet %>% filter(interaction == 'np') %>% nrow,
          .before = 2)

write_csv(all_netindex_final, 'output_tables/Supplementary_table_4.csv')
```

# Supplementary Figure 8

```{r}
module_belong <- single_net_df %>% 
  select(ID = name, module, origin) %>% 
  left_join(bin_code) %>% 
  distinct()

shared_module <- map(c('Dry', 'Wet'), function(net){
  module_list <- module_belong %>% 
    filter(origin == net) %>% 
    pull(module) %>% 
    unique()
  
  res_module <- map(module_list, function(mod){
    nodes_in_mod <- module_belong %>% 
      filter(origin == net,
             module == mod)
    
    num_nodes <- nrow(nodes_in_mod)
    
    detailed_filter <- detailed_results_filtered %>% 
      mutate(donor = str_remove(donor, '_genes_model'),
             receiver = str_remove(receiver, '_genes_model')) %>% 
      filter(receiver %in% nodes_in_mod$Genome & donor %in% nodes_in_mod$Genome) %>%
      # filter((receiver %in% nodes_in_mod$Genome & !(donor %in% nodes_in_mod$Genome)) |
      #          (!(receiver %in% nodes_in_mod$Genome) & donor %in% nodes_in_mod$Genome)) %>% 
      group_by(compound) %>% 
      count() %>% 
      left_join(classified_df)
    
    if(nrow(detailed_filter) < 1){
      detailed_filter <- tibble(compound = 'M_meoh_e',
                                group = 'alcohol',
                                n = NA_real_)
    }  
    
    detailed_filter <- detailed_filter %>% 
      mutate(group = ifelse(is.na(group), 'other', group),
             origin = net,
             module = glue::glue('{mod} ({nnodes} MAGs)',
                                 mod = mod,
                                 nnodes = num_nodes))
    
  }) %>% reduce(rbind)
  
}) %>% reduce(rbind)

modules_sort <- jamba::mixedSort(unique(shared_module$module))

shared_module_plot <- shared_module %>% 
  drop_na(n) %>% 
  mutate(module = factor(module, levels = modules_sort),
         compound = str_remove(compound, '_e$'),
         compound = str_remove(compound, '^M_')) %>% 
  left_join(bigg_metabolites, by = c('compound' = 'universal_bigg_id')) %>% 
  ggplot() +
  geom_tile(aes(x = module,
                y = name,
                fill = n),
            color = 'white') +
  scale_fill_viridis_c(option = 'A', direction = -1, na.value = 'white') +
  facet_grid(cols = vars(origin),
             rows = vars(group),
             scales = 'free',
             space = 'free',
             switch = 'y') +
  theme_bw() +
  labs(fill = 'Number of times\nshared') +
  custom_theme +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        panel.grid = element_blank(),
        strip.text.y.left = element_text(angle = 0),
        strip.placement = 'outer',
        strip.background = element_blank(),
        axis.title = element_blank(),
        axis.text.y = element_text(size = 3),
        panel.spacing = unit(0.1, 'lines'),
        legend.key.height = unit(2, 'lines'))

shared_module_plot
```


```{r}
num_shared_wit_out <- map(c('Dry', 'Wet'), function(net){
  module_list <- module_belong %>% 
    filter(origin == net) %>% 
    pull(module) %>% 
    unique()
  
  res_module <- map(module_list, function(mod){
    nodes_in_mod <- module_belong %>% 
      filter(origin == net,
             module == mod) %>% 
      pull(Genome)
    
    sharing_per_bin <- map(nodes_in_mod, function(bin){
      
      mip <- global_filtered %>% 
        filter(MAG_1 == bin | MAG_2 == bin) %>%
        mutate(bin_checked = bin,
               other_bin = ifelse(MAG_1 == bin, MAG_2, MAG_1),
               sharing_type = ifelse(other_bin %in% nodes_in_mod,
                                     'Within module',
                                     'Outside module')) %>% 
        filter(!is.na(mip)) %>% 
        group_by(bin_checked, sharing_type) %>% 
        summarize(mean_mip = mean(mip))
      
      per_bin <- detailed_results_filtered %>% 
        mutate(donor = str_remove(donor, '_genes_model'),
               receiver = str_remove(receiver, '_genes_model')) %>% 
        filter(receiver == bin | donor == bin) %>%
        mutate(bin_checked = bin,
               other_bin = ifelse(donor == bin, receiver, donor),
               sharing_type = ifelse(other_bin %in% nodes_in_mod,
                                     'Within module',
                                     'Outside module')) %>% 
        group_by(bin_checked, other_bin, sharing_type) %>% 
        count(name = 'num_shared_metabolites') %>% 
        group_by(bin_checked, sharing_type) %>% 
        mutate(num_bins_sharing_with = n()) %>% 
        summarize(mean_shared = mean(num_shared_metabolites))
      
      if(nrow(per_bin) == 0){
        per_bin <- tibble(bin_checked = rep(bin, 2),
                          sharing_type = c('Within module',
                                           'Outside module'),
                          mean_shared = c(0,0))
      }
      
      return(per_bin)
      
    }) %>% reduce(rbind) %>% 
      mutate(origin = net,
             module = mod)
    
  }) %>% reduce(rbind)
  
}) %>% reduce(rbind)


num_shared_plot <- num_shared_wit_out %>% 
  filter(mean_shared != 0) %>% 
  ggplot(aes(x = sharing_type,
             y = mean_shared)) +
  geom_jitter(aes(color = sharing_type),
              size = .6,
              alpha = 0.5) +
  geom_violin(aes(fill = sharing_type),
              alpha = 0.3) +
  facet_wrap2(~origin,
              strip = strip_nested()) +
  labs(y = 'Mean number of metabolites shared') +
  custom_theme +
  theme(axis.title.x = element_blank(),
        legend.position = 'none',
        plot.title = element_blank())

num_shared_plot
```

```{r}
shared_net <-  map(c('Dry', 'Wet'), function(net){
  bins_net <- module_belong %>% 
    filter(origin == net) %>% 
    pull(Genome) 
  
  detailed_filter <- detailed_results_filtered %>% 
    mutate(donor = str_remove(donor, '_genes_model'),
           receiver = str_remove(receiver, '_genes_model')) %>% 
    filter(receiver %in% bins_net & donor %in% bins_net) %>% 
    left_join(classified_df) %>% 
    mutate(group = ifelse(is.na(group), 'other', group)) %>% 
    select(donor, receiver, group) %>% 
    mutate(both_ordered = map2_chr(donor, receiver, function(x, y){
      str_c(sort(c(x, y)), collapse = '--')
    })) %>% 
    select(both_ordered, group) %>% 
    distinct() %>% 
    group_by(group) %>% 
    count() %>% 
    mutate(origin = net)
}) %>% reduce(rbind)

shared_net_plot <- shared_net %>% 
  ggplot(aes(x = group,
             y = n,
             fill = origin)) +
  geom_col(color = 'black',
           linewidth = .1,
           position = position_dodge()) +
  labs(y = 'Number of MAG pairs',
       fill = 'Network') +
  scale_fill_manual(values = c('orange2', 'steelblue')) +
  custom_theme +
  theme(legend.position = 'bottom',
        axis.text.x = element_text(angle = 45, hjust = 1, size = 5),
        axis.title.x = element_blank(),
        legend.key.size = unit(0.2, 'lines'),
        legend.box.spacing = unit(0, 'lines'),
        legend.margin = margin(0, 0, 0, 0, 'lines'))



shared_net_plot
```

## Uniting figure

```{r}

des <- "
AA
BC
"
  
  
supp_8 <- shared_module_plot + free(num_shared_plot) + free(shared_net_plot) +
  plot_layout(ncol = 1,
              heights = c(4, 1),
              widths = c(1, 3),
              design = des) +
  plot_annotation(tag_levels = 'A')


ggsave('output_figures/Supplementary_Figure_8.svg', dpi = 300,
       units = 'mm', height = 185, width = 180)

ggsave('output_figures/Supplementary_Figure_8.png', dpi = 300,
       units = 'mm', height = 185, width = 180)
```


